\section{The Debt Ledger Model}
\label{sec:ledger}

\subsection{Core Concepts}

The debt ledger model organizes proof obligations into three categories:

\begin{definition}[Paid Obligation]
An obligation is \emph{paid} if it can be mechanically verified from artifacts
in the repository without assuming any unproven conjecture.
\end{definition}

\begin{definition}[Unpaid Obligation]
An obligation is \emph{unpaid} if its satisfaction requires proving a statement
equivalent in difficulty to RH (or another open problem).
\end{definition}

\begin{definition}[Rung]
A \emph{rung} is a discrete step in the verification ladder, consisting of:
\begin{itemize}
  \item A contract specifying what the rung establishes and what it does NOT claim.
  \item Artifacts providing evidence (equations, digests, signatures).
  \item A verifier script that checks the rung's integrity.
  \item A release tag for reproducibility.
\end{itemize}
\end{definition}

\subsection{The NA0 Debt Framing}

The key insight is that any bound of the form
\[
  |\pi(x) - \operatorname{li}(x)| < f(x)
\]
for all $x > x_0$ requires controlling the contribution of zeta zeros.
The ``tail'' contribution from zeros with large imaginary part cannot be bounded
without RH or an equivalent statement.

We call this the \textbf{NA0 debt}: the obligation to bound the tail contribution
from infinitely many zeros. This debt remains unpaid.

See \texttt{proof\_artifacts/R7\_BOUND\_STATEMENT/R7\_BOUND\_STATEMENT.md} for
the explicit statement of the bound and its dependencies.

\subsection{Artifact Chain}

Each rung produces artifacts that feed into subsequent rungs:
\begin{enumerate}
  \item R4--R6: Equation inventory, error bound components, parameter choices.
  \item R7: Explicit bound statement citing R4--R6.
  \item R8: Regeneration of equation inventory for comparison.
  \item R9: Input manifest with frozen digests.
  \item R10: Assembly receipt (root hash over all inputs).
  \item R11--R18: Signature layers (GPG, post-quantum hybrid).
  \item R20: Deterministic rebuild of assembly root.
  \item R21: Deterministic rebuild of release zip.
  \item R22: Rung index and status ledger.
\end{enumerate}

See \texttt{RUNG\_INDEX.md} for the complete map.
