\section{Results So Far}
\label{sec:results}

We summarize what the verification ladder has established.

\subsection{Paid Obligations}

The following obligations have been paid (mechanically verified):

\begin{enumerate}
  \item \textbf{Classical signature (GPG):} Dave's detached signature over the
        R10 assembly root.
        See \texttt{proof\_artifacts/R11\_SIGNATURE/sigs/dave.asc}.

  \item \textbf{Post-quantum hybrid signature:} P-384 + ML-DSA-65 signature
        over the assembly root.
        See \texttt{proof\_artifacts/R15\_PQ\_SIGNATURE/sigs\_pq/}.

  \item \textbf{Assembly root rebuild:} Deterministic regeneration of R10
        from the verify surface.
        See \texttt{VERIFY\_R20\_REBUILD\_ASSEMBLY\_ROOT.sh}.

  \item \textbf{Release reproducibility:} Deterministic zip rebuild from git tag.
        See \texttt{scripts/rebuild\_release\_zip.sh}.

  \item \textbf{Key fingerprint capture:} GPG fingerprint recorded for attribution.
        See \texttt{proof\_artifacts/R14\_KEY\_CAPTURE/captures/}.

  \item \textbf{PQ tooling receipt:} Backend and version captured for PQ signatures.
        See \texttt{proof\_artifacts/R16\_PQ\_TOOLING/}.
\end{enumerate}

\subsection{Verification Coverage}

The main verifier runs 23 steps:
\begin{itemize}
  \item Steps 1--11: Repository integrity (git status, required files, redaction,
        exhibits, contribution ledger).
  \item Steps 12--23: Rung verifiers (R4--R20).
\end{itemize}

To run verification:
\begin{verbatim}
VR_STRICT=1 ./VERIFY.sh
\end{verbatim}

Expected output:
\begin{verbatim}
=== VERIFICATION PASSED ===
\end{verbatim}

\subsection{What This Means}

The verification ladder establishes that:
\begin{enumerate}
  \item The equation inventory, error bounds, and parameter choices are
        frozen and reproducible.
  \item The assembly root hash is deterministic.
  \item Signed attestations are cryptographically bound to the artifacts.
  \item Release zips can be rebuilt identically from git tags.
\end{enumerate}

This provides \emph{infrastructure} for tracking proof obligations, but does
NOT prove any mathematical claim about $\pi(x)$ or RH.
