\section{Limits and Remaining Obligations}
\label{sec:limits}

This section explicitly states what remains unpaid and why.

\subsection{The Tail Bound Obligation}

The central unpaid obligation is the \textbf{tail bound}: controlling the
contribution of zeta zeros $\rho = \beta + i\gamma$ with $|\gamma| > T$
for any fixed $T$.

Any bound of the form
\[
  |\psi(x) - x| < C \sqrt{x} \log^2 x
\]
requires summing over \emph{all} zeros. The sum converges, but its size depends
on the location of zeros. Without knowing that all zeros lie on the critical
line, the tail cannot be bounded effectively.

\textbf{Status:} UNPAID. Equivalent in difficulty to RH.

See \texttt{proof\_artifacts/R7\_BOUND\_STATEMENT/R7\_BOUND\_STATEMENT.md}
for the explicit statement of where this debt enters.

\subsection{Remaining Obligations}

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Item} & \textbf{Status} & \textbf{Notes} \\
\hline
Tail bound proof & UNPAID & The dragon is boxed, not slain \\
RH claim & NOT MADE & This repo makes no claim regarding RH \\
Proof reproduction & NOT DONE & No proofs are reproduced \\
External audit & NOT DONE & Third-party review pending \\
\hline
\end{tabular}
\end{center}

\subsection{Why This Matters}

The debt ledger model makes explicit a common source of errors in mathematical
claims: conflating ``we have organized the pieces'' with ``we have proven the
result.'' By explicitly recording unpaid obligations, we prevent scope creep
and premature claims.

The infrastructure is valuable even with unpaid debt because it:
\begin{enumerate}
  \item Provides a clear target for future work.
  \item Ensures that any future claim of progress can be verified against
        the frozen artifacts.
  \item Maintains an audit trail for reproducibility.
\end{enumerate}

\subsection{What Would Pay the Debt}

The tail bound obligation would be paid by either:
\begin{enumerate}
  \item A proof of RH (establishing all zeros have $\beta = \frac{1}{2}$).
  \item An unconditional zero-density estimate sufficient for the required bound.
  \item A fundamentally different approach that avoids the explicit sum over zeros.
\end{enumerate}

None of these is claimed or implied by this work.
